Update on Spatio-angular Transfer Functions

### 2018-03-12 slides/2018-03-12-group-meeting/group_meeting.tex
Group meeting slides w/ group theory.

\usetheme{simple}
\usecolortheme{}
\usefonttheme{serif}
\useinnertheme{}
\useoutertheme{}
\author{Talon Chandler}
\date{March 5, 2018}
\title{Spatio-angular Transfer Functions}

@@

\maketitle
\begin{frame}[label=sec-1]{$x$-oriented dipole point spread function}
 \begin{center}
   \includegraphics[width=0.8\textwidth]{figs/x.png}
 \end{center}
\end{frame}

\begin{frame}[label=sec-1]{$z$-oriented dipole point spread function}
 \begin{center}
   \includegraphics[width=0.8\textwidth]{figs/z.png}
 \end{center}
\end{frame}

\begin{frame}[label=sec-1]{Point spread functions---Novotny}
 \begin{center}
   \includegraphics[width=0.8\textwidth]{figs/z.png}
 \end{center}
\end{frame}

\begin{frame}[label=sec-1]{Point spread functions---Novotny}
 \begin{center}
   \includegraphics[width=0.8\textwidth]{figs/nov-psf.png}
 \end{center}
\end{frame}

\begin{frame}[label=sec-1]{Only two spherical harmonics in the paraxial spatio-angular point spread function}
 \begin{center}
   \includegraphics[width=0.7\textwidth]{figs/sh.png}
 \end{center}
\end{frame}

\begin{frame}{Paraxial spatio-angular point spread function}
\begin{align*}
      h^*(\rd{}; \mathbf{r}_o, \so{}) \propto ({I_0^*}^2 + 2{I_1^*}^2)Y_0^0(\so{}) + \frac{1}{\sqrt{5}}\left(-{I_0^*}^2 + 4{I_1^*}^2\right)Y_2^{0}(\so{})\label{eq:para}
\end{align*}
\begin{align*}
  {I_0^*} = \left(\frac{\text{NA}}{n_o}\right)^2\left[\frac{2J_1(\tilde{r}_d)}{\tilde{r}_d}\right],
  \hspace{2em}
  {I_1^*} = \left(\frac{\text{NA}}{n_o}\right)^3\left[\frac{2J_2(\tilde{r}_d)}{\tilde{r}_d}\right],
  \end{align*}
  \begin{align*}
  \tilde{r}_d = \frac{2\pi\text{NA}\thinspace r_d}{M\lambda},\hspace{2em}
  \text{NA} = n_o\sin\theta_{\text{max}},\hspace{2em}
  M = \frac{n_o}{n_b}\frac{f_t}{f_o}.
\end{align*}
\end{frame}

\begin{frame}[label=sec-1]{Paraxial spatio-angular PSF and OTF}
 \begin{center}
   \includegraphics[width=1.0\textwidth]{figs/ft.pdf}
 \end{center}
\end{frame}

\begin{frame}[label=sec-1]{Scalar optics transfer functions---Mertz, Goodman}
 \begin{center}
   \includegraphics[width=.7\textwidth]{figs/mertz.jpg}
 \end{center}
\end{frame}

\begin{frame}[label=sec-1]{Electromagnetic optics transfer functions}
\tikzstyle{block} = [draw, fill=white, rectangle, 
    minimum height=2cm, minimum width=3cm, text width=2cm, align=center]
\tikzstyle{sum} = [draw, fill=white, circle, node distance=4cm]
\tikzstyle{input} = [coordinate]
\tikzstyle{output} = [coordinate]
\tikzstyle{pinstyle} = [pin edge={to-,thin,black}]
\begin{tikzpicture}[auto, node distance=3cm,>=latex]
    \node [input, name=input] {};
    \node [block, align=center] (csf) {CSF\\ $\mb{e}_d(\rd{};\ro{}, \so{})$};
    \node [block,  right of=csf, node distance=6cm] (ctf) {CTF\\ $\mb{e}_b(\rb{};\ro{}, \so{})$};
    \node [block, below of=ctf, node distance=4cm] (otf) {OTF\\ $H_l^m(\bs{\nu})$};
    \node [block, below of=csf, node distance=4cm] (psf) {PSF\\ $h(\ro{}, \so{})$};

    \draw [<->] (csf) -- node[name=u, text width=3cm, align=center] {Tube Lens\\ $\mathcal{F}_{\mathbb{R}^2}$} (ctf);        
    \draw [->] (ctf) -- node[name=v, right] {$\mathcal{F}_{\mathbb{S}^2}[\mb{e}_b\star_{\mathbb{R}^2} \mb{e}_b]$} (otf);
    \draw [<->] (psf) -- node[below] {$\mathcal{F}_{\mathbb{R}^3\times\mathbb{S}^2}$} (otf);
    \draw [->] (csf) -- node[name=v, text width=3cm, align=center, left] {Detector\\ $|\mb{e}_d(\rd{};\ro{}, \so{})|^2_{\mathbb{R}^2}$} (psf);
      \end{tikzpicture}
\end{frame}

>>>>

\usetheme{simple}
\usecolortheme{}
\usefonttheme{serif}
\useinnertheme{}
\useoutertheme{}
\author{Talon Chandler}
\date{March 12, 2018}
\title{Update on Spatio-angular Transfer Functions}

@@

\maketitle
\begin{frame}[label=sec-1]{Steady progress on closed form OTF}
  \begin{itemize}
  \item Initial calculation didn't match my numerical OTF.
  \item Found some issues that I glossed over. Calculation still in progress.
  \end{itemize}
\end{frame}

\begin{frame}[label=sec-1]{Brute-force degeneracy finding}
 \begin{center}
   \includegraphics[width=0.8\textwidth]{figs/solid-angle-uncertainty.png}
 \end{center}
\end{frame}

\begin{frame}[label=sec-1]{0.8 NA Epi-illumination Microscope}
 \begin{center}
   \includegraphics[width=0.8\textwidth]{figs/singular-value-spectrum-epi.pdf}
 \end{center}
\end{frame}

\begin{frame}[label=sec-1]{0.8 NA Symmetric diSPIM Microscope}
 \begin{center}
   \includegraphics[width=0.8\textwidth]{figs/singular-value-spectrum-dispim.pdf}
 \end{center}
\end{frame}

\begin{frame}[label=sec-1]{Group theory for finding degeneracy}
\begin{columns}
  \begin{column}{0.5\textwidth}
    \centering \textbf{Quantum mechanics}\\\vspace{2em}
    $\mathcal{H} = \text{Hamiltonian}$\\\vspace{2em}
    $\mathcal{H}\psi_k = W_k\psi_k$\\\vspace{2em}
    $\mathcal{T}_j\mathcal{H} - \mathcal{H}\mathcal{T}_j = 0$\\\vspace{2em}
    $\mathcal{T}_j$ form the symmetry group of the Hamiltonian.
\end{column}
\begin{column}{0.5\textwidth}  %%<--- here
  \centering \textbf{Imaging}\\\vspace{2em}
  $\mathcal{H} = \text{Forward operator}$\vspace{2em}
  $\mathcal{H}^{\dagger}\mathcal{H}u_k = \mu_ku_k$\\\vspace{2em}
  $\mathcal{T}_j\mathcal{H}^{\dagger}\mathcal{H} - \mathcal{H}^{\dagger}\mathcal{H}\mathcal{T}_j = 0$\\\vspace{2em}
  $\mathcal{T}_j$ form the symmetry group of the imaging system.

\end{column}
\end{columns}
\end{frame}
